Bird beak's elaboration and exploration: data preparation

### 2022-06-14 Analysis/01-Data_preparation.Rmd
Update 01-Data_preparation.Rmd

>>>>

## Passeriformes focus

```{r}
## Get the traitspace for all passeriformes
load("../Data/Processed/shapespace_allbirds_lvl_superorder_order.rda")
clades_list <- as.data.frame(read.csv("../Data/Raw/BirdClades.csv", row.names = 1, stringsAsFactors = TRUE))
shapespace_passeriformes <- shapespace_allbirds_lvl_superorder_order[[1]]$space[(clades_list[, "level2_order"] == "Passeriformes"), ]

## Loading the Passeriformes clades
load("../Data/Processed/clade.info_passerines.rda")
## Clean the levels
shapespace_passeriformes$level1 <- rep("", nrow(shapespace_passeriformes))
shapespace_passeriformes$level2 <- rep("", nrow(shapespace_passeriformes))

## Fill in the level1
for(clade in 1:length(clade_info_passerines$passerine_big_clades)) {
  clade_name <- names(clade_info_passerines$passerine_big_clades)[clade]
  shapespace_passeriformes[clade_info_passerines$passerine_big_clades[[clade]], "level1"] <- clade_name
}
## Fill in the level2
for(clade in 1:length(clade_info_passerines$passerine_small_clades)) {
  clade_name <- names(clade_info_passerines$passerine_small_clades)[clade]
  shapespace_passeriformes[clade_info_passerines$passerine_small_clades[[clade]], "level2"] <- clade_name
}
shapespace_passeriformes[, "level1"] <- as.factor(shapespace_passeriformes[, "level1"])
shapespace_passeriformes[, "level2"] <- as.factor(shapespace_passeriformes[, "level2"])

## Do the prep data from here (with all the trees! ouch!)
shapespace_passeriformes_two_levels <- prep.data(
                                          level = 0, lvl.inc = c(1,2),
                                          clades    = shapespace_passeriformes[, c("level1", "level2")],
                                          space     = shapespace_passeriformes,
                                          dim       = 1:8,
                                          consensus = consensus_tree,
                                          trees     = trees_list,
                                          verbose   = TRUE)
save(shapespace_passeriformes_two_levels, file = "../Data/Processed/shapespace_passeriformes_two_levels.rda")
```
